### 2020-10-27 Thesis-Chapter3-PolicyMaking.tex
Refine OODA proposal

The \ac{OODAloop} was a developed by Air Force Colonel John Boyd in the context of military strategy, but its ideas have
penetrated many other sectors \cite{angerman_2004}. Boyd created it as a description of a successful strategy for
countering opponents in real-time combat. There is an emphasis on speed and ``getting inside'' your opponent's loop. It
is illustrated in \myfig{fig-ooda-loop}.

@@

The \ac{OODAloop} serves as a good basis for contending with \acp{wicked-prob} because it has the correct fundamental
structure. It maps very well to the \ac{classical-method} steps of problem definition (orientation), ideation and
analysis (orientation), decision, and action, but it emphasizes the \ac{incrementalism}'s iteration and feedback.
Additionally, while policymaking doesn't share the pace of real-time combat, in other ways the metaphor holds up. This
is the idea behind language like the ``war on drugs''---whether combating armed opponents or \acp{wicked-prob}, one is
contending with an unpredictable opponent in an environment lacking complete information with an unlimited set of
possible actions.

The \ac{OODAloop} as is does not have all the properties listed in \mysec{sec-policy-lessons}, however.
... %TODO: finish this
See \myfig{fig-policy-ooda-loop}.

@@

>>>>

The \ac{OODAloop} was a developed by Air Force Colonel John Boyd as a description of a successful strategy for
countering opponents in real-time combat \cite{angerman_2004}. Boyd created it in the context of military strategy, but
its ideas have penetrated many other sectors, including cybersecurity, where it serves as a model for structuring
incident response \cite{schneier_future_2014}. There is an emphasis on speed and ``getting inside'' your opponent's
loop. It is illustrated in \myfig{fig-ooda-loop}.

@@

The \ac{OODAloop} serves as a good basis for contending with \acp{wicked-prob} because it has the correct fundamental
structure. It maps very well to the \ac{classical-method} steps of problem definition (orientation), ideation and
analysis (orientation), decision, and action, but it emphasizes the \ac{incrementalism}'s iteration and feedback.
Additionally, while policymaking doesn't share the pace of real-time combat, in other ways the metaphor of facing an
unpredictable opponent in a dynamic environment where every action counts holds up.

The one modification the \ac{OODAloop} needs is unification of the problem definition and analysis steps. This is
Rittel's ``argumentative process in the course of which an image of the problem and of the solution emerges gradually''
\cite{rittel_dilemmas_1973}. \myfig{fig-policy-ooda-loop} illustrates the \ac{OODAloop} modified to serve as a
policymaking strategy.

@@

% Note on using argument maps to facilitate this argumentative process

% Summarize chapter: wicked problems, why normal methods fail, how this strategy works

% Preview it in action in the following chapters
